### 2016-02-12 mcmc.tex
Fix minor typos.

In a probabilistic inference, the posterior pdf $p(\pars\given\data)$,
or pdf for the parameters $\pars$ given the data $\data$, is
constructed from the likelihood $p(\data\given\pars)$, or pdf for the
data given the parameters, and the prior pdf $p(\pars)$ for the
parameters by what's often known as ``Bayes rule'',
\begin{eqnarray}
p(\pars\given\data) &=& \frac{1}{Z}\,p(\data\given\pars)\,p(\pars)
\label{eq:bayes}\quad .
\end{eqnarray}
In these contexts, the constant $Z$, sometimes written as
$p(\data)$, is known by the names ``evidence'', ``marginal likelihood'',
``Bayes integral'', and ``prior predictive probability'', and is usually
\emph{extremely hard to calculate}.\note{Some would call
  the factor $Z$ in \equationname~(\ref{eq:bayes}) something like
  ``$p(\data)$'' or ``the fully marginalized likelihood'' or the 
  probability of the data.
  Of course it is only the probability of the data within the model
  space under consideration!
  We (intend to) discuss this object and these issues elsewhere
  (in various things in preparation).
  The factor $Z$ is often hugely difficult to compute, because the
  likelihood (or the prior) can have extremely complex structure,
  with multiple arbitrarily compact modes, arbitrarily positioned
  in the (presumably high dimensional) parameter space $\pars$.
  Elsewhere, we discuss the computation of this object (\citealt{fengji}),
  and so have many others before us.
  Perhaps more importantly, we also have views about why you probably never really
  \emph{want} to compute it.
  These views relate to the fact that the value of this integral
  very rarely delivers the answer to a question you care about (see future \documentname s in this series).
  These philosophical matters and the computational issues are both
  outside the scope of this \documentname,
  but suffice it to say:
  If the computation of $Z$ is in your travel plans, you will need yto
  think about implementing some non-trivial integrating or sampling
  technology; we will give some brief description of options in
  \sectionname~\ref{sec:methods}.}
That is, you often know the function $p(\pars\given\data)$ up to a
constant factor; you can compute ratios of the pdf at pairs of points,
but not the precise value at any individual point.

@@

Both of these reasons for using \MCMC---that it is a parameter-space
search algorithm, and that it is a simple-to-code effective
optimizer---are \emph{not good reasons}.  \MCMC\ is first and foremost a
\emph{sampler}.  If you are trying to find the optimum of the
likelihood or the posterior pdf, you should use an \emph{optimzer},
not a sampler.  If you want to make sure you search all of parameter
space, you should use a \emph{search algorithm}, not a sampler.  \MCMC\ 
is good at one thing, and one thing only: Sampling ill-normalized (or
otherwise hard to sample) pdfs.

@@

The reason that there is no simple answer is that you can't really
ever know that you have sampled the full posterior pdf, and the reason
for \emph{that} is that if you \emph{could} know that, you would also
be able to solve the famously difficult discrete optimization
problem.\note{Famously, there is ``no free lunch''
  \citep{nofreelunch}: You can't find the global optimum of a general
  optimization problem without exhastive search of all possibilities.
  This is very closely related---somehow---to the difficulty of sampling.}
Another way to put it is that you might have two modes---two separated
regions of substantial total probability---in the posterior pdf that
are both important but separated by a large region of low probability.
If you are using a simple sampler, you could sample one of these modes
very well but the sampler will take effectively infinite time to find
the other mode.
Any test of convergence would be passed, but in fact the sampling
would be incomplete and not representative.
That is, knowing that you have a complete and representative sampling
is effectively impossible.

>>>>

In a probabilistic inference, the posterior pdf $p(\pars\given\data)$,
or pdf for the parameters $\pars$ given the data $\data$, is
constructed from the likelihood $p(\data\given\pars)$, or pdf for the
data given the parameters, and the prior pdf $p(\pars)$ for the
parameters by what's often known as ``Bayes rule'',
\begin{eqnarray}
p(\pars\given\data) &=& \frac{1}{Z}\,p(\data\given\pars)\,p(\pars)
\label{eq:bayes}\quad .
\end{eqnarray}
In these contexts, the constant $Z$, sometimes written as
$p(\data)$, is known by the names ``evidence'', ``marginal likelihood'',
``Bayes integral'', and ``prior predictive probability'', and is usually
\emph{extremely hard to calculate}.\note{Some would call
  the factor $Z$ in \equationname~(\ref{eq:bayes}) something like
  ``$p(\data)$'' or ``the fully marginalized likelihood'' or the 
  probability of the data.
  Of course it is only the probability of the data within the model
  space under consideration!
  We (intend to) discuss this object and these issues elsewhere
  (in various things in preparation).
  The factor $Z$ is often hugely difficult to compute, because the
  likelihood (or the prior) can have extremely complex structure,
  with multiple arbitrarily compact modes, arbitrarily positioned
  in the (presumably high dimensional) parameter space $\pars$.
  Elsewhere, we discuss the computation of this object (\citealt{fengji}),
  and so have many others before us.
  Perhaps more importantly, we also have views about why you probably never really
  \emph{want} to compute it.
  These views relate to the fact that the value of this integral
  very rarely delivers the answer to a question you care about (see future \documentname s in this series).
  These philosophical matters and the computational issues are both
  outside the scope of this \documentname,
  but suffice it to say:
  If the computation of $Z$ is in your travel plans, you will need to
  think about implementing some non-trivial integrating or sampling
  technology; we will give some brief description of options in
  \sectionname~\ref{sec:methods}.}
That is, you often know the function $p(\pars\given\data)$ up to a
constant factor; you can compute ratios of the pdf at pairs of points,
but not the precise value at any individual point.

@@

Both of these reasons for using \MCMC---that it is a parameter-space
search algorithm, and that it is a simple-to-code effective
optimizer---are \emph{not good reasons}.  \MCMC\ is first and foremost a
\emph{sampler}.  If you are trying to find the optimum of the
likelihood or the posterior pdf, you should use an \emph{optimizer},
not a sampler.  If you want to make sure you search all of parameter
space, you should use a \emph{search algorithm}, not a sampler.  \MCMC\ 
is good at one thing, and one thing only: Sampling ill-normalized (or
otherwise hard to sample) pdfs.

@@

The reason that there is no simple answer is that you can't really
ever know that you have sampled the full posterior pdf, and the reason
for \emph{that} is that if you \emph{could} know that, you would also
be able to solve the famously difficult discrete optimization
problem.\note{Famously, there is ``no free lunch''
  \citep{nofreelunch}: You can't find the global optimum of a general
  optimization problem without exhaustive search of all possibilities.
  This is very closely related---somehow---to the difficulty of sampling.}
Another way to put it is that you might have two modes---two separated
regions of substantial total probability---in the posterior pdf that
are both important but separated by a large region of low probability.
If you are using a simple sampler, you could sample one of these modes
very well but the sampler will take effectively infinite time to find
the other mode.
Any test of convergence would be passed, but in fact the sampling
would be incomplete and not representative.
That is, knowing that you have a complete and representative sampling
is effectively impossible.
